---
title: "Charity Brand-Equity Architectures: Main Analysis"
subtitle: "EFA → CFA → SEM comparison of Faircloth, Boenigk & Becker, and Ríos Romero et al."
# author left blank for double-anonymised submission
date: today
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    df-print: kable
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
  cache: true        # cache expensive SEM fits
params:
  primary_estimator: "MLR"      # continuous outcomes / higher-order structural
  ordinal_estimator: "WLSMV"    # ordinal measurement models
  primary_amount_outcome: "OF02_02_num_log"     # annual donation (log)
  secondary_amount_outcome: "OF02_01_num_log"   # most-recent donation (log)
  binary_outcome: "OF_Spender"                  # donor status
  ses_mode: "none"              # "none" | "outcome" | "latent_outcome"
  rebuild_data: false           # TRUE to rebuild fragebogen from raw via build_fragebogen()
  data_source: "auto"           # "auto" | "api" | "local" (see R/90_load_data_pipeline.R)
---

```{r}
#| label: setup
#| include: false
source(here::here("R", "00_paths.R"))
source(here::here("R", "01_packages.R"))
source(here::here("R", "12_lavaan_models.R"))   # model registry (works today)
source(here::here("R", "11_fit_helpers.R"))   # SEM_REGISTRY, coerce_sem_data(), ordered_vars_for_estimator()
source(here::here("R", "20_fit_cfa.R"))
source(here::here("R", "21_fit_sem.R"))
source(here::here("R", "40_tables.R"))

# Reproducible context-source selection (avoid heuristic; see R/10_datasets.R)
# SEM_DEBUG_CONTEXT_SOURCE_NAME <- "fragebogen$qnr1"
# Source pipeline (always — gives us build_fragebogen() and config)
source(here::here("R", "90_load_data_pipeline.R"))

# Rebuild fragebogen from raw if requested (or if derived data absent)
if (params$rebuild_data || !file.exists(DATEN_STANDARDISIERT)) {
  build_fragebogen(rebuild = params$rebuild_data, source = params$data_source)
}

source(here::here("R", "10_datasets.R"))         # builds DATASETS = list(fc,bo,ro,cross)
stopifnot(exists("DATASETS"))
```

# Overview

This document reproduces the **main** analysis: measurement quality and
higher-order structure for the three architectures, and their criterion-related
evidence against donation outcomes. Diagnostics (HTMT, CMV, ICC, invariance,
deviations, robustness) live in `02_supplements_addendum.qmd`.

Datasets in `DATASETS`: `fc`, `bo`, `ro`, `cross`. Outcomes:
`r params$primary_amount_outcome` (primary), `r params$secondary_amount_outcome`,
`r params$binary_outcome`.

# Sample and data audit

```{r}
#| label: dataset-audit
audit <- readr::read_csv(file.path(CSV_DIR, "01_dataset_audit.csv"),
                         show_col_types = FALSE)
gt::gt(audit) |> gt::tab_header("Dataset registry audit")
```

# Confirmatory factor analysis

```{r}
#| label: cfa-fits
cfa_specs <- list(
  fc_higher = list(syntax = cfa_fc_higher_order_original(), data = DATASETS$fc),
  fc_coreB  = list(syntax = cfa_fc_core_B(),                 data = DATASETS$fc),
  bo        = list(syntax = cfa_bo_original(),               data = DATASETS$bo),
  ro        = list(syntax = cfa_ro_original(),               data = DATASETS$ro)
)

cfa_fit_tbl <- purrr::imap_dfr(cfa_specs, function(s, id) {
  fit <- fit_cfa(s$syntax, s$data, estimator = params$ordinal_estimator,
                 model_id = id)
  tidy_fit(fit, model_id = id, estimator = params$ordinal_estimator)
})
save_table(cfa_fit_tbl, "paper_table_cfa_fit")
gt_fit_summary(cfa_fit_tbl, "CFA fit by architecture")
```

# Structural models and explained variance

```{r}
#| label: sem-fits
sem_specs <- list(
  fc = list(builder = sem_fc_original, data = DATASETS$fc),
  bo = list(builder = sem_bo_original, data = DATASETS$bo),
  ro = list(builder = sem_ro_original, data = DATASETS$ro)
)
outcomes <- c(params$primary_amount_outcome,
              params$secondary_amount_outcome,
              params$binary_outcome)

sem_r2_tbl <- purrr::imap_dfr(sem_specs, function(s, id) {
  purrr::map_dfr(outcomes, function(oc) {
    is_binary <- is_binary_outcome(oc, s$data)   # from 11_fit_helpers.R
    fit <- fit_sem(s$builder, s$data, outcome = oc, ses_mode = params$ses_mode,
                   estimator = if (is_binary) params$ordinal_estimator else params$primary_estimator,
                   model_id = paste0(id, "_", oc))
    # ordered= handled inside fit_sem via ordered_vars_for_estimator()
    sem_paths_r2(fit, outcome = oc, model_id = paste0(id, "_", oc))
  })
})
save_table(sem_r2_tbl, "paper_table_structural_paths_r2")
gt::gt(sem_r2_tbl) |> gt::tab_header("Structural paths and R² (identical-case discipline applies; see supplement)")
```

> **Note on comparability.** Model-specific samples differ; the directly
> comparable evidence is the identical-case analysis (see supplement §Sampling).
> R² across non-equivalent solutions is indicative only.

# Session info {.unnumbered}

```{r}
#| label: sessioninfo
sessionInfo()
```
