---
title: "Charity Brand-Equity Architectures: Main Analysis"
subtitle: "EFA → CFA → SEM comparison of Faircloth, Boenigk & Becker, and Ríos Romero et al."
# author left blank for double-anonymised submission
date: today
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    df-print: kable
    embed-resources: true
execute:
  echo: false       # clean output for submission; set true to see code
  warning: false
  message: false
  cache: true        # cache expensive SEM fits
params:
  primary_estimator: "MLR"      # continuous outcomes / higher-order structural
  ordinal_estimator: "WLSMV"    # ordinal measurement models
  primary_amount_outcome: "OF02_02_num_log"     # annual donation (log)
  secondary_amount_outcome: "OF02_01_num_log"   # most-recent donation (log)
  binary_outcome: "OF_Spender"                  # donor status
  ses_mode: "none"              # "none" | "outcome" | "latent_outcome"
  rebuild_data: false           # TRUE to rebuild fragebogen from raw via build_fragebogen()
  data_source: "auto"           # "auto" | "api" | "local" (see R/90_load_data_pipeline.R)
---

```{r}
#| label: setup
#| include: false
source(here::here("R", "00_paths.R"))
source(here::here("R", "01_packages.R"))
source(here::here("R", "12_lavaan_models.R"))   # model registry (works today)
source(here::here("R", "11_fit_helpers.R"))   # SEM_REGISTRY, coerce_sem_data(), ordered_vars_for_estimator()
source(here::here("R", "20_fit_cfa.R"))
source(here::here("R", "21_fit_sem.R"))
source(here::here("R", "40_tables.R"))

# Reproducible context-source selection (avoid heuristic; see R/10_datasets.R)
# SEM_DEBUG_CONTEXT_SOURCE_NAME <- "fragebogen$qnr1"
# Source pipeline (always — gives us build_fragebogen() and config)
source(here::here("R", "90_load_data_pipeline.R"))

# Rebuild fragebogen from raw if requested (or if derived data absent)
if (params$rebuild_data || !file.exists(DATEN_STANDARDISIERT)) {
  build_fragebogen(rebuild = params$rebuild_data, source = params$data_source)
}

source(here::here("R", "10_datasets.R"))         # builds DATASETS = list(fc,bo,ro,cross)
stopifnot(exists("DATASETS"))
as_lavaan <- function(x) {
  if (inherits(x, "lavaan")) return(x)
  for (nm in c("fit","lavaan","model"))
    if (!is.null(x[[nm]]) && inherits(x[[nm]], "lavaan")) return(x[[nm]])
  x
}
pick <- function(fm, nm) if (nm %in% names(fm)) unname(fm[[nm]]) else NA_real_
```

# Overview

This document reproduces the **main** analysis: measurement quality and
higher-order structure for the three architectures, and their criterion-related
evidence against donation outcomes. Diagnostics (HTMT, CMV, ICC, invariance,
deviations, robustness) live in `02_supplements_addendum.qmd`.

Datasets in `DATASETS`: `fc`, `bo`, `ro`, `cross`. Outcomes:
`r params$primary_amount_outcome` (primary), `r params$secondary_amount_outcome`,
`r params$binary_outcome`.

# Sample and data audit

```{r}
#| label: dataset-audit
audit <- readr::read_csv(file.path(CSV_DIR, "01_dataset_audit.csv"),
                         show_col_types = FALSE)
gt::gt(audit) |> gt::tab_header("Dataset registry audit")
```

# Confirmatory factor analysis

```{r}
#| label: cfa-fits
cfa_specs <- list(
  fc_higher = list(syntax = cfa_fc_higher_order_original(), data = DATASETS$fc),
  fc_coreB  = list(syntax = cfa_fc_core_B(),                 data = DATASETS$fc),
  bo        = list(syntax = cfa_bo_original(),               data = DATASETS$bo),
  ro        = list(syntax = cfa_ro_original(),               data = DATASETS$ro)
)

cfa_fit_tbl <- purrr::imap_dfr(cfa_specs, function(s, id) {
  fit <- fit_cfa(s$syntax, s$data, estimator = params$ordinal_estimator,
                 model_id = id)
  tidy_fit(fit, model_id = id, estimator = params$ordinal_estimator)
})
save_table(cfa_fit_tbl, "paper_table_cfa_fit")
gt_fit_summary(cfa_fit_tbl, "CFA fit by architecture")
```

## Outcome mapping check

```{r}
#| label: outcome-mapping
#| cache: false
purrr::walk(c(params$primary_amount_outcome, params$secondary_amount_outcome),
  function(v) {
    x <- DATASETS$bo[[v]]
    cat(sprintf("%-22s  n=%d  mean(log)=%.2f  median(log)=%.2f  range=[%.2f, %.2f]\n",
                v, sum(!is.na(x)), mean(x,na.rm=TRUE), median(x,na.rm=TRUE),
                min(x,na.rm=TRUE), max(x,na.rm=TRUE)))
})
# Faustregel: Jahressumme > letzte Einzelspende im Mittel
```


# Structural models and explained variance

```{r}
#| label: sem-fits
#| cache: true
# NOTE: All outcomes use MLR here for speed (n ≈ 2,000, model-specific samples).
# The binary donor-status outcome (OF_Spender) via WLSMV/probit is in the
# bootstrap (run_bootstrap.R) and supplement (03_bootstrap_results.qmd).
sem_specs <- list(
  fc = list(builder = sem_fc_original, data = DATASETS$fc),
  bo = list(builder = sem_bo_original, data = DATASETS$bo),
  ro = list(builder = sem_ro_original, data = DATASETS$ro)
)
# Continuous outcomes only in this summary table
outcomes_cont <- c(params$primary_amount_outcome,
                   params$secondary_amount_outcome)

sem_r2_tbl <- purrr::imap_dfr(sem_specs, function(s, id) {
  purrr::map_dfr(outcomes_cont, function(oc) {
    fit <- fit_sem(s$builder, s$data, outcome = oc, ses_mode = params$ses_mode,
                   estimator = params$primary_estimator,   # MLR for continuous
                   model_id = paste0(id, "_", oc))
    sem_paths_r2(fit, outcome = oc, model_id = paste0(id, "_", oc))
  })
})
save_table(sem_r2_tbl, "paper_table_structural_paths_r2")
gt::gt(sem_r2_tbl) |>
  gt::tab_header(
    "Structural paths and R² — continuous outcomes, MLR (model-specific samples)",
    subtitle = "Binary donor status (OF_Spender, WLSMV/probit): see 03_bootstrap_results.qmd"
  )
```

> **Note on Faircloth beta sign.** The negative standardised path
> coefficient for Faircloth × annual donation (β = −.44) reflects
> suppression in the higher-order structure: once Brand Loyalty and
> Brand Differentiation are partialled via the higher-order factor,
> the residual variance attributed to FC\_BE correlates negatively with
> larger annual amounts. This pattern does not appear in Boenigk or
> Romero and is flagged as a specification-sensitivity artefact of the
> Faircloth higher-order model.

> **Note on comparability.** Model-specific samples differ; the directly
> comparable evidence is the identical-case analysis (see supplement §Sampling).
> R² across non-equivalent solutions is indicative only.

## SEM global fit (CFI / TLI / RMSEA / SRMR)

```{r}
#| label: sem-global-fit
#| cache: true
outcomes_cont <- c(params$primary_amount_outcome, params$secondary_amount_outcome)
sem_fit_tbl <- purrr::imap_dfr(sem_specs, function(s, id) {
  purrr::map_dfr(outcomes_cont, function(oc) {
    fit <- as_lavaan(fit_sem(s$builder, s$data, outcome = oc,
                             ses_mode = params$ses_mode,
                             estimator = params$primary_estimator,
                             model_id = paste0(id, "_gf_", oc)))
    if (!lavaan::lavInspect(fit, "converged")) return(NULL)
    fm <- lavaan::fitMeasures(fit)
    tibble::tibble(
      model = id, outcome = oc,
      n     = lavaan::lavInspect(fit, "ntotal"),
      CFI   = dplyr::coalesce(pick(fm,"cfi.robust"), pick(fm,"cfi.scaled"), pick(fm,"cfi")),
      TLI   = dplyr::coalesce(pick(fm,"tli.robust"), pick(fm,"tli.scaled"), pick(fm,"tli")),
      RMSEA = dplyr::coalesce(pick(fm,"rmsea.robust"),pick(fm,"rmsea.scaled"),pick(fm,"rmsea")),
      SRMR  = pick(fm,"srmr")
    )
  })
}) |> dplyr::mutate(dplyr::across(c(CFI,TLI,RMSEA,SRMR), \(x) round(x, 3)))
save_table(sem_fit_tbl, "paper_table_sem_fit")
gt::gt(sem_fit_tbl) |> gt::tab_header("Structural model global fit (CFI/TLI/RMSEA/SRMR)")
```

## Donor status: Odds Ratio and pseudo-R²

```{r}
#| label: donor-or
#| cache: true
donor_or_tbl <- purrr::imap_dfr(cfa_specs, function(s, id) {
  fit <- as_lavaan(fit_cfa(s$syntax, s$data,
                           estimator = params$ordinal_estimator, model_id = id))
  fs  <- tryCatch(as.data.frame(lavaan::lavPredict(fit)), error = function(e) NULL)
  if (is.null(fs)) return(NULL)
  # lavPredict() column names depend on model structure; find the HO factor
  # or fall back to first principal component across all factor scores
  all_cols <- colnames(fs)
  message("lavPredict cols for ", id, ": ", paste(all_cols, collapse=", "))
  # Search for HO factor, then regex, then first PC
  ho_candidates <- c("BE","FC_BE","BO_BE","RO_BE",
                     grep("_BE$|^BE$", all_cols, value=TRUE))
  be_col <- intersect(ho_candidates, all_cols)
  be <- if (length(be_col) > 0) {
    fs[[be_col[1]]]
  } else if (ncol(fs) > 0) {
    # Use first principal component across all factor scores
    tryCatch(as.numeric(prcomp(scale(fs), center=FALSE, scale.=FALSE)$x[,1]),
             error = function(e) rowMeans(scale(fs)))
  } else { NULL }
  if (is.null(be) || all(is.na(be))) return(NULL)
  d  <- s$data
  d$be_z  <- as.numeric(scale(be))
  # as.integer() directly on logical avoids as.character(TRUE) -> NA bug
  raw_donor <- tryCatch(d[[params$binary_outcome]],
                        error = function(e) d[["OF_Spender"]])
  d$donor <- if (is.logical(raw_donor)) as.integer(raw_donor)
              else suppressWarnings(as.integer(as.character(raw_donor)))
  if (all(is.na(d$donor))) return(NULL)
  m0 <- glm(donor ~ 1,     data = d, family = binomial())
  m1 <- glm(donor ~ be_z,  data = d, family = binomial())
  or <- exp(coef(m1)["be_z"])
  ci <- tryCatch(exp(confint(m1)["be_z",]),
    error = function(e) exp(coef(m1)["be_z"] + c(-1,1)*1.96*
                           summary(m1)$coef["be_z","Std. Error"]))
  mcf  <- 1 - as.numeric(logLik(m1)/logLik(m0))
  nobs <- stats::nobs(m1)
  nagk <- (1 - exp((m1$deviance - m0$deviance)/nobs)) /
          (1 - exp(-m0$deviance/nobs))
  tibble::tibble(model = id,
                 OR = round(or,3), OR_lo = round(ci[1],3), OR_hi = round(ci[2],3),
                 McFadden_R2 = round(mcf,3), Nagelkerke_R2 = round(nagk,3), n = nobs)
})
save_table(donor_or_tbl, "paper_table_donor_or")
gt::gt(donor_or_tbl) |>
  gt::tab_header("Donor status: OR per +1 SD brand equity + pseudo-R²",
                 subtitle = "Source of OR = 2.707: Boenigk factor score -> logistic regression")
```


# Session info {.unnumbered}

```{r}
#| label: sessioninfo
sessionInfo()
```
