---
title: "Supplementary Material & Addendum"
subtitle: "CMV, HTMT, ICC, invariance, deviations from preregistration, robustness"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    df-print: kable
    embed-resources: true
  pdf:
    toc: true
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
params:
  primary_estimator: "MLR"
  ordinal_estimator: "WLSMV"
  run_clf: false        # latent common-method-factor (may not converge for Boenigk)
---

```{r}
#| label: setup
#| include: false
source(here::here("R", "00_paths.R"))
source(here::here("R", "01_packages.R"))
source(here::here("R", "12_lavaan_models.R"))
source(here::here("R", "30_diagnostics_htmt.R"))
source(here::here("R", "31_diagnostics_cmv.R"))
source(here::here("R", "32_diagnostics_icc.R"))
source(here::here("R", "33_invariance.R"))
source(here::here("R", "40_tables.R"))

# Pipeline reference data (org_synonyme, fields, skalen, skalen_SEM, source_links)
source(here::here("R", "pipeline", "external_Sources.R"))
source(here::here("R", "10_datasets.R"))    # DATASETS = list(fc, bo, ro, cross)
stopifnot(exists("DATASETS"))

# ------------------------------------------------------------------------------
# Construct → item maps (derived from skalen + 01_lavaan_models.R)
# NOTE: FC_BS and FC items use recoded reversed columns (_rev) — these must
# already exist in DATASETS$fc after recode_reversed_items() has been applied
# in build_fragebogen(). TOM and SAW come from the awareness extraction pipeline.
# ------------------------------------------------------------------------------
construct_items_bo <- list(
  BO_TR = c("B101_01","B101_02","B101_03"),
  BO_CO = c("B102_01","B102_02","B102_03")
)

construct_items_fc <- list(
  FC_BR = c("FC01_01","FC01_02","FC01_03"),
  FC_BD = c("FC01_04","FC01_05","FC01_06"),
  FC_BC = c("FC02_01","FC02_02","FC02_03","FC02_04","FC02_05","FC02_06","FC02_07","FC02_08"),
  FC_BS = c("FC02_09","FC02_10_rev","FC02_11","FC02_12_rev"),
  FC_BF = c("FC03_01","FC03_02","FC03_03"),
  FC_RC = c("TOM","SAW")
)

construct_items_ro <- list(
  RO_BF = c("R201_01","R201_02","R201_03","R201_04"),
  RO_BS = c("R201_05","R201_06","R201_07"),
  RO_BI = c("R202_01","R202_02","R202_03","R202_04"),
  RO_BA = c("R202_05","R202_06","R202_07","R202_08"),
  RO_BD = c("R203_01","R203_02","R203_03","R203_04","R203_05"),
  RO_BR = c("R203_06","R203_07","R203_08","R203_09"),
  RO_AC = c("R204_01","R204_02","R204_03","R204_04"),
  RO_EC = c("R204_05","R204_06","R204_07","R204_08","R204_09"),
  RO_ID = c("R205_01","R205_02","R205_03","R205_04","R205_05","R205_06","R205_07")
)

save_t <- function(t, n) {
  readr::write_csv(t, file.path(CSV_DIR, paste0(n, ".csv")), na=""); t
}
```

# Organisations and sampling frame

```{r}
#| label: org-overview
gt::gt(org_synonyme[, c("org_id","org_name")]) |>
  gt::tab_header("Table S1. Austrian NPOs evaluated (n = 26)",
                 subtitle = "Full synonym lists available in R/pipeline/external_Sources.R")
```

```{r}
#| label: source-links
gt::gt(source_links) |>
  gt::tab_header("Table S2. Recruitment channel overview")
```

# Sample and non-independence

```{r}
#| label: dataset-sizes
audit <- readr::read_csv(file.path(CSV_DIR, "01_dataset_audit.csv"),
                         show_col_types = FALSE)
gt::gt(audit) |> gt::tab_header("Table S3. Dataset registry audit")
```

```{r}
#| label: icc
#| eval: false
# ICC for the nested structure (requires an organisation id column; add once
# BA03_01 → organisation label join is done in the pipeline).
# icc_crossed(DATASETS$cross, response="OF02_02_num_log",
#             group1="REF", group2="BA03_01")
```

# Discriminant validity (HTMT)

```{r}
#| label: htmt-bo
htmt_bo <- htmt_manual(DATASETS$bo, construct_items_bo)
save_t(htmt_bo, "S_htmt_boenigk")
gt::gt(htmt_bo) |>
  gt::tab_header("Table S4. Boenigk HTMT (Trust × Commitment)",
                 subtitle = "< .85 acceptable | .85–.90 borderline | > .90 problematic") |>
  gt::fmt_number(columns = c(HTMT, heterotrait_mean, monotrait_1_mean, monotrait_2_mean),
                 decimals = 3)
```

```{r}
#| label: htmt-fc
# Filter to columns present in DATASETS$fc (TOM/SAW may be absent until
# awareness pipeline runs; use available items only)
fc_items_present <- construct_items_fc
fc_items_present <- lapply(fc_items_present,
  function(its) its[its %in% names(DATASETS$fc)])
fc_items_present <- fc_items_present[sapply(fc_items_present, length) >= 2]

htmt_fc <- htmt_manual(DATASETS$fc, fc_items_present)
save_t(htmt_fc, "S_htmt_faircloth")
gt::gt(htmt_fc) |>
  gt::tab_header("Table S5. Faircloth HTMT",
                 subtitle = "Expected borderline: FC_F1 (FC_BR/FC_BD) × FC_F2 (FC_BC/FC_BS)") |>
  gt::fmt_number(columns = c(HTMT, heterotrait_mean, monotrait_1_mean, monotrait_2_mean),
                 decimals = 3)
```

```{r}
#| label: htmt-ro
htmt_ro <- htmt_manual(DATASETS$ro, construct_items_ro)
save_t(htmt_ro, "S_htmt_romero")
gt::gt(htmt_ro) |>
  gt::tab_header("Table S6. Romero HTMT",
                 subtitle = "Expected problematic (> .90): RO_BA–RO_BD, RO_BF–RO_BS, RO_BD–RO_BR") |>
  gt::fmt_number(columns = c(HTMT, heterotrait_mean, monotrait_1_mean, monotrait_2_mean),
                 decimals = 3)
```

```{r}
#| label: htmt-summary
htmt_counts <- dplyr::bind_rows(
  htmt_summary_counts(htmt_bo, "Boenigk & Becker"),
  htmt_summary_counts(htmt_fc, "Faircloth"),
  htmt_summary_counts(htmt_ro, "Romero et al.")
)
save_t(htmt_counts, "S_htmt_summary_counts")
gt::gt(htmt_counts) |> gt::tab_header("Table S7. HTMT interpretation counts by architecture")
```

# Common method variance

```{r}
#| label: cmv-harman
harman_tbl <- dplyr::bind_rows(
  harman_single_factor(
    DATASETS$bo, items = unlist(construct_items_bo),
    label = "Boenigk Core Architecture"),
  harman_single_factor(
    DATASETS$fc,
    items = unlist(fc_items_present),
    label = "Faircloth Brand Architecture"),
  harman_single_factor(
    DATASETS$ro, items = unlist(construct_items_ro),
    label = "Romero Complex Architecture")
)
save_t(harman_tbl, "S_cmv_harman")
gt::gt(harman_tbl) |>
  gt::tab_header("Table S8. Harman's single-factor test",
                 subtitle = "Deliberately weak diagnostic; CFA comparison (Table S9) is more informative") |>
  gt::fmt_number(columns = harman_first_var_pct, decimals = 2)
```

```{r}
#| label: cmv-cfa-bo
cmv_bo <- cmv_cfa_comparison(
  trait_model = cfa_bo_original(),
  data        = DATASETS$bo,
  items       = unlist(construct_items_bo),
  estimator   = params$ordinal_estimator,
  ordered     = unlist(construct_items_bo),
  run_clf     = params$run_clf
)
save_t(cmv_bo, "S_cmv_cfa_boenigk")
gt::gt(cmv_bo) |>
  gt::tab_header("Table S9a. CFA-based CMV comparison — Boenigk",
                 subtitle = "Single-factor CFI expected near .414 vs theoretical .997") |>
  gt::fmt_number(columns = c(chisq, CFI, TLI, RMSEA, SRMR), decimals = 3) |>
  gt::sub_missing(missing_text = "—")
```

```{r}
#| label: cmv-cfa-fc
cmv_fc <- cmv_cfa_comparison(
  trait_model = cfa_fc_higher_order_original(),
  data        = DATASETS$fc,
  items       = unlist(fc_items_present),
  estimator   = params$ordinal_estimator,
  ordered     = unlist(fc_items_present),
  run_clf     = params$run_clf
)
save_t(cmv_fc, "S_cmv_cfa_faircloth")
gt::gt(cmv_fc) |>
  gt::tab_header("Table S9b. CFA-based CMV comparison — Faircloth") |>
  gt::fmt_number(columns = c(chisq, CFI, TLI, RMSEA, SRMR), decimals = 3) |>
  gt::sub_missing(missing_text = "—")
```

```{r}
#| label: cmv-cfa-ro
cmv_ro <- cmv_cfa_comparison(
  trait_model = cfa_ro_original(),
  data        = DATASETS$ro,
  items       = unlist(construct_items_ro),
  estimator   = params$ordinal_estimator,
  ordered     = unlist(construct_items_ro),
  run_clf     = params$run_clf
)
save_t(cmv_ro, "S_cmv_cfa_romero")
gt::gt(cmv_ro) |>
  gt::tab_header("Table S9c. CFA-based CMV comparison — Romero") |>
  gt::fmt_number(columns = c(chisq, CFI, TLI, RMSEA, SRMR), decimals = 3) |>
  gt::sub_missing(missing_text = "—")
```

# Multi-group invariance (donor vs non-donor)

```{r}
#| label: invariance-bo
#| error: true
inv_bo <- tryCatch(invariance_steps(
  model      = cfa_bo_original(),
  data       = DATASETS$bo,
  group      = "OF_Spender",
  estimator  = params$ordinal_estimator,
  ordered    = unlist(construct_items_bo)
), error = function(e) { message("invariance-bo failed: ", e$message); NULL })
if (!is.null(inv_bo)) save_t(inv_bo, "S_invariance_boenigk")
gt::gt(inv_bo) |>
  gt::tab_header("Table S10a. Measurement invariance — Boenigk (donor vs non-donor)",
                 subtitle = "Chen (2007): metric/scalar supported if ΔCFI ≥ −.010") |>
  gt::fmt_number(columns = c(CFI, RMSEA, dCFI, dRMSEA), decimals = 3) |>
  gt::sub_missing(missing_text = "—")
```

```{r}
#| label: invariance-fc
#| eval: false
# inv_fc <- invariance_steps(cfa_fc_higher_order_original(), DATASETS$fc,
#                            group="OF_Spender", estimator=params$ordinal_estimator,
#                            ordered=unlist(fc_items_present))
```

```{r}
#| label: invariance-ro
#| eval: false
# inv_ro <- invariance_steps(cfa_ro_original(), DATASETS$ro,
#                            group="OF_Spender", estimator=params$ordinal_estimator,
#                            ordered=unlist(construct_items_ro))
```

# Validation overview

> Run this section interactively with the live `validated` object (produced by
> `validate_data()` inside `build_fragebogen()`), or render with
> `rebuild_data: true` so the pipeline runs first.

```{r}
#| label: validation-overview
#| eval: false
# Requires: validated (from build_fragebogen()), config (from settings.R)
source(here::here("R", "pipeline", "settings.R"))
source(here::here("R", "pipeline", "validierung_uebersicht.R"))
# Produces: summary_table (gt) + scorer histogram per questionnaire type
```

```{r}
#| label: validation-summary-table
#| eval: false
# If validated is already in scope:
library(dplyr); library(tibble); library(tidyr)
get_qnr_thresholds <- function(qnr, config) {
  q_cfg <- config$validation$by_qnr[[qnr]]
  list(min_valid_ratio      = q_cfg$min_valid_ratio %||% NA,
       min_duration_q       = q_cfg$min_duration_q  %||% NA,
       max_duration_mult    = config$validation$global$max_duration_multiplier,
       min_score            = config$validation$global$min_score)
}
validated %>%
  group_by(QUESTNNR) %>%
  summarise(n = n(),
            pct_valid        = round(100*mean(is_valid, na.rm=TRUE), 1),
            avg_scorer       = round(mean(scorer,       na.rm=TRUE), 2),
            pct_valid_ratio  = round(100*mean(valid_ratio_score, na.rm=TRUE), 1),
            pct_duration_ok  = round(100*mean(duration_score,    na.rm=TRUE), 1),
            pct_alt_flag     = round(100*mean(alt_score < 0,      na.rm=TRUE), 1),
            .groups = "drop") %>%
  gt::gt() %>%
  gt::tab_header("Table S0. Validation summary by questionnaire type",
                 subtitle = "is_valid threshold: scorer >= 1")
```

# R² difference bootstrap (S20)

> Bootstrap results are produced separately via `run_bootstrap.R`
> (see repo root). Once `outputs/csv/supplements/S20_r2_difference_bootstrap_all_levels.csv`
> exists, render `analysis/03_bootstrap_results.qmd` to produce Table S11.

# Deviations from the preregistration {#sec-deviations}

**Registered plan:** *Triple Replication Study*, OSF (pre-analysis, post-survey
registration; data collected May–July 2025, registered before analysis;
anonymised view-only link in main text). The registered plan was fixed before
model estimation. The registration governs the *replication* of a single
higher-order path (Brand Equity → Donation Intention); the present manuscript
reuses the same data for a measurement-defensibility comparison and is a
**largely exploratory re-framing** (Bekkers et al., 2025).

| # | Registered plan | As implemented | Type | Rationale |
|---|---|---|---|---|
| 1 | Estimator: MLR primary; WLSMV robustness. | **WLSMV primary** for ordinal measurement models; robust ML for continuous outcomes. | Justified deviation | WLSMV is appropriate for ordinal Likert indicators. |
| 2 | EFA: PAF + varimax. | **Polychoric + OLS** (`psych::fa`); parallel analysis / VSS. | Justified deviation | Correct treatment for ordinal data. |
| 3 | Discriminant validity not specified; comparison via adj. R², ΔCFI/TLI, AIC/BIC. | **HTMT** as primary discriminant criterion. | Exploratory addition | Romero overlap (max HTMT ≈ .96) is therefore exploratory. |
| 4 | Outcome: Brand Equity → Donation Intention (β ≈ .40–.60). | **Realised giving** (most-recent; annual, log) + binary donor status; intention reserved. | Different / expanded | Dashboard question requires behavioural outcomes. |
| 5 | Exclusion: > 60% missing. | **80% / 90% completeness** thresholds. | Justified (stricter) | More conservative analytic sample. |
| 6 | Replication of one higher-order path. | **Architecture-level comparison** → layered dashboard. | Exploratory re-framing | Extends beyond the registered replication. |

**Consistent with the registration:** Austrian online survey, May–July 2025;
>20-organisation, ~2,000-respondent design; constructive-replication logic;
power rationale (Wolf et al., 2013); CFI/TLI/RMSEA/SRMR thresholds;
multi-group reliability/validity across donor/non-donor segments.

# Robustness

```{r}
#| label: robustness-ses
#| eval: false
# SES-adjusted structural models: ses_mode = "outcome"
# source(here::here("R", "21_fit_sem.R"))
# fit_sem(sem_bo_original, DATASETS$bo, outcome="OF02_02_num_log", ses_mode="outcome")
```

```{r}
#| label: robustness-alt-structures
#| eval: false
# Alternative Faircloth structures: Core B and Purified A
# fit_cfa(cfa_fc_core_B(),      DATASETS$fc, estimator=params$ordinal_estimator, model_id="fc_coreB")
# fit_cfa(cfa_fc_purified_A(),  DATASETS$fc, estimator=params$ordinal_estimator, model_id="fc_purA")
```

# Session info {.unnumbered}

```{r}
#| label: sessioninfo
sessionInfo()
```

# References {.unnumbered}

Bekkers, R., Chapman, C. M., Prosser, A. M. B., Wiepking, P., & Meyer, M.
(2025). Let us be clear: Why and how to demonstrate data and methods
transparency in nonprofit research. *VOLUNTAS, 36*(4), 473–482.
https://doi.org/10.1007/s11266-025-00736-0
