---
title: "Supplementary Material & Addendum"
subtitle: "CMV, HTMT, ICC, invariance, deviations from preregistration, robustness"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    df-print: kable
    embed-resources: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    papersize: a4
    geometry: margin=2.5cm
    keep-tex: false
    include-in-header:
      text: |
        \usepackage{booktabs}
        \usepackage{longtable}
        \usepackage{array}
        \usepackage{caption}
        \captionsetup[table]{skip=4pt}
execute:
  echo: true
  warning: false
  message: false
  freeze: auto       # skip re-execution if source unchanged
params:
  primary_estimator: "MLR"
  ordinal_estimator: "WLSMV"
  run_clf: false        # latent common-method-factor (may not converge for Boenigk)
---

```{r}
#| label: setup
#| include: false
source(here::here("R", "00_paths.R"))
source(here::here("R", "01_packages.R"))
source(here::here("R", "12_lavaan_models.R"))
source(here::here("R", "20_fit_cfa.R"))       # fit_cfa(), tidy_fit(), reliability_ave()
source(here::here("R", "21_fit_sem.R"))       # fit_sem(), sem_paths_r2()
source(here::here("R", "30_diagnostics_htmt.R"))
source(here::here("R", "31_diagnostics_cmv.R"))
source(here::here("R", "32_diagnostics_icc.R"))
source(here::here("R", "33_invariance.R"))
source(here::here("R", "40_tables.R"))

# PDF-safe table helper: kable for LaTeX, gt for HTML
print_tbl <- function(df, title = NULL, subtitle = NULL, digits = 3) {
  if (knitr::is_latex_output()) {
    cap <- if (!is.null(title)) title else ""
    knitr::kable(df, digits = digits, caption = cap,
                 format = "latex", booktabs = TRUE,
                 linesep = "") |>
      kableExtra::kable_styling(
        latex_options = c("scale_down", "hold_position"),
        font_size = 8)
  } else {
    tbl <- gt::gt(df)
    if (!is.null(title)) tbl <- gt::tab_header(tbl, title = title, subtitle = subtitle)
    tbl
  }
}

# Pipeline reference data (org_synonyme, fields, skalen, skalen_SEM, source_links)
source(here::here("R", "pipeline", "external_Sources.R"))
source(here::here("R", "10_datasets.R"))    # DATASETS = list(fc, bo, ro, cross)
stopifnot(exists("DATASETS"))

# cfa_specs needed by reliability and nested comparison chunks
cfa_specs <- list(
  fc_higher = list(syntax = cfa_fc_higher_order_original(), data = DATASETS$fc),
  fc_coreB  = list(syntax = cfa_fc_core_B(),                data = DATASETS$fc),
  bo        = list(syntax = cfa_bo_original(),              data = DATASETS$bo),
  ro        = list(syntax = cfa_ro_original(),              data = DATASETS$ro)
)
as_lavaan <- function(x) {
  if (inherits(x, "lavaan")) return(x)
  for (nm in c("fit","lavaan","model"))
    if (!is.null(x[[nm]]) && inherits(x[[nm]], "lavaan")) return(x[[nm]])
  x
}
pick <- function(fm, nm) if (nm %in% names(fm)) unname(fm[[nm]]) else NA_real_

# ------------------------------------------------------------------------------
# Construct → item maps (derived from skalen + 01_lavaan_models.R)
# NOTE: FC_BS and FC items use recoded reversed columns (_rev) — these must
# already exist in DATASETS$fc after recode_reversed_items() has been applied
# in build_fragebogen(). TOM and SAW come from the awareness extraction pipeline.
# ------------------------------------------------------------------------------
construct_items_bo <- list(
  BO_TR = c("B101_01","B101_02","B101_03"),
  BO_CO = c("B102_01","B102_02","B102_03"),
  BO_BF = c("BC03_01","BC03_02","BC03_03"),  # Brand Familiarity/Awareness
  BO_RC = c("TOM","SAW")                      # Top-of-Mind + Spontaneous Awareness
)

construct_items_fc <- list(
  FC_BR = c("FC01_01","FC01_02","FC01_03"),
  FC_BD = c("FC01_04","FC01_05","FC01_06"),
  FC_BC = c("FC02_01","FC02_02","FC02_03","FC02_04","FC02_05","FC02_06","FC02_07","FC02_08"),
  FC_BS = c("FC02_09","FC02_10_rev","FC02_11","FC02_12_rev"),
  FC_BF = c("FC03_01","FC03_02","FC03_03"),
  FC_RC = c("TOM","SAW")
)

construct_items_ro <- list(
  RO_BF = c("R201_01","R201_02","R201_03","R201_04"),
  RO_BS = c("R201_05","R201_06","R201_07"),
  RO_BI = c("R202_01","R202_02","R202_03","R202_04"),
  RO_BA = c("R202_05","R202_06","R202_07","R202_08"),
  RO_BD = c("R203_01","R203_02","R203_03","R203_04","R203_05"),
  RO_BR = c("R203_06","R203_07","R203_08","R203_09"),
  RO_AC = c("R204_01","R204_02","R204_03","R204_04"),
  RO_EC = c("R204_05","R204_06","R204_07","R204_08","R204_09"),
  RO_ID = c("R205_01","R205_02","R205_03","R205_04","R205_05","R205_06","R205_07")
)

save_t <- function(t, n) {
  readr::write_csv(t, file.path(CSV_DIR, paste0(n, ".csv")), na=""); t
}
```

```{r}
#| label: pdf-gt-hook
#| include: false
# Register knit_print override for gt objects when rendering to PDF
if (knitr::is_latex_output()) {
  knit_print.gt_tbl <- function(x, ...) {
    x <- gt::tab_options(x,
      table.width             = gt::pct(100),
      table.font.size         = gt::px(8),
      column_labels.font.size = gt::px(8),
      data_row.padding        = gt::px(1))
    latex_out <- gt::as_latex(x)
    knitr::asis_output(as.character(latex_out))
  }
  registerS3method("knit_print", "gt_tbl", knit_print.gt_tbl,
                   envir = asNamespace("knitr"))
}
```


# Item wording, source mappings and model syntax {#sec-items}

Full German item wording, recoding rules and lavaan model syntax are available
in the research compendium at `R/12_lavaan_models.R` and `R/external_Sources.R`
([research compendium — blinded for review]). The table below provides the
English-language item descriptions and construct assignments.

```{r}
#| label: item-mapping
#| cache: false
tibble::tibble(
  Architecture = c(
    rep("Faircloth (2005)", 18),
    rep("Boenigk & Becker (2016)", 8),
    rep("Rios Romero et al. (2023)", 40)
  ),
  Construct = c(
    # Faircloth
    rep("FC_BR: Brand Recall", 3),
    rep("FC_BD: Brand Differentiation", 3),
    rep("FC_BC: Brand Commitment", 8),
    rep("FC_BF: Brand Familiarity", 3),
    rep("FC_BR: Brand Recall (TOM + SAW)", 1),
    # Boenigk
    rep("BO_TR: Brand Trust", 3),
    rep("BO_CO: Brand Commitment", 3),
    rep("BO_RC: Brand Recall (TOM + SAW)", 1),
    rep("BO_BF: Brand Familiarity", 1),
    # Romero
    rep("RO_BF: Brand Familiarity", 4),
    rep("RO_BS: Brand Strength", 3),
    rep("RO_BI: Brand Identification", 4),
    rep("RO_BW: Brand Authenticity", 4),
    rep("RO_BD: Brand Differentiation", 5),
    rep("RO_BR: Brand Reputation", 4),
    rep("RO_AC: Attitudinal Commitment", 4),
    rep("RO_EC: Emotional Commitment", 5),
    rep("RO_ID: Brand Identification", 7)
  ),
  Item = c(
    # Faircloth FC_BR (FC01_01-03)
    "FC01_01: I recognise [org] among other charitable organisations",
    "FC01_02: I can recall [org] when I think of charitable organisations",
    "FC01_03: [org] comes to mind quickly when I think of charities",
    # FC_BD (FC01_04-06)
    "FC01_04: [org] is clearly different from other organisations",
    "FC01_05: [org] stands out among charitable organisations",
    "FC01_06: [org] has a distinctive profile",
    # FC_BC (FC02_01-08)
    "FC02_01: [org] has a good character",
    "FC02_02: [org] has a trustworthy character",
    "FC02_03: [org] is socially responsible",
    "FC02_04: [org] is a caring organisation",
    "FC02_05: [org] has a strong personality",
    "FC02_06: [org] projects a positive image",
    "FC02_07: [org] makes a good impression",
    "FC02_08: [org] has a respectable image",
    # FC_BF (FC03_01-03)
    "FC03_01: I am familiar with [org]",
    "FC03_02: I know [org] well",
    "FC03_03: I have knowledge about [org]",
    # AW
    "TOM/SAW: Unaided and aided awareness items (0=not heard of, ..., open recall)",
    # Boenigk BO_TR (B101_01-03)
    "B101_01: I trust [org]",
    "B101_02: [org] is reliable",
    "B101_03: [org] is honest in its dealings",
    # BO_CO (B102_01-03)
    "B102_01: I feel a long-term connection to [org]",
    "B102_02: I am committed to [org]",
    "B102_03: My relationship with [org] is important to me",
    # AW
    "TOM/SAW: Shared awareness items (same as Faircloth)",
    # BO_BF (BC03_01-03 — available for organisations with brand familiarity battery)
    "BC03: Brand familiarity scale (available for selected organisations)",
    # Romero RO_BF (R201_01-04)
    "R201_01: I am familiar with [org]",
    "R201_02: I have knowledge about [org]",
    "R201_03: I know what [org] stands for",
    "R201_04: I am informed about [org]",
    # RO_BS (R201_05-07)
    "R201_05: [org] is a well-known organisation",
    "R201_06: [org] is a leading organisation in its field",
    "R201_07: [org] has a strong presence",
    # RO_BI (R202_01-04)
    "R202_01: [org] has a good image",
    "R202_02: [org] has a positive reputation among the public",
    "R202_03: People think well of [org]",
    "R202_04: [org] is viewed favourably",
    # RO_BA (R202_05-08)
    "R202_05: [org] is associated with positive values",
    "R202_06: [org] is linked to good causes",
    "R202_07: [org] represents something positive",
    "R202_08: [org] has associations I approve of",
    # RO_BD (R203_01-05)
    "R203_01: [org] is different from other organisations",
    "R203_02: [org] offers something unique",
    "R203_03: [org] is distinctive",
    "R203_04: [org] stands out",
    "R203_05: [org] has a unique profile",
    # RO_BR (R203_06-09)
    "R203_06: [org] is relevant to me",
    "R203_07: [org] matters to people like me",
    "R203_08: [org] addresses issues important to me",
    "R203_09: [org] is meaningful to me personally",
    # RO_AC (R204_01-04)
    "R204_01: I support [org] regularly",
    "R204_02: I am committed to [org] in the long term",
    "R204_03: I intend to continue my relationship with [org]",
    "R204_04: I plan to stay connected to [org]",
    # RO_EC (R204_05-09)
    "R204_05: I feel emotionally connected to [org]",
    "R204_06: [org] means a lot to me",
    "R204_07: I care about [org]",
    "R204_08: I feel personally attached to [org]",
    "R204_09: My relationship with [org] is emotionally significant",
    # RO_ID (R205_01-07)
    "R205_01: I identify with [org]",
    "R205_02: [org] reflects who I am",
    "R205_03: I share the values of [org]",
    "R205_04: [org] is part of my identity",
    "R205_05: Being associated with [org] says something about me",
    "R205_06: I see myself in [org]",
    "R205_07: [org] represents people like me"
  ),
  `Source variable` = c(
    "FC01_01","FC01_02","FC01_03",
    "FC01_04","FC01_05","FC01_06",
    "FC02_01","FC02_02","FC02_03","FC02_04","FC02_05","FC02_06","FC02_07","FC02_08",
    "FC03_01","FC03_02","FC03_03",
    "TOM / SAW",
    "B101_01","B101_02","B101_03",
    "B102_01","B102_02","B102_03",
    "TOM / SAW",
    "BC03_01-03",
    "R201_01","R201_02","R201_03","R201_04",
    "R201_05","R201_06","R201_07",
    "R202_01","R202_02","R202_03","R202_04",
    "R202_05","R202_06","R202_07","R202_08",
    "R203_01","R203_02","R203_03","R203_04","R203_05",
    "R203_06","R203_07","R203_08","R203_09",
    "R204_01","R204_02","R204_03","R204_04",
    "R204_05","R204_06","R204_07","R204_08","R204_09",
    "R205_01","R205_02","R205_03","R205_04","R205_05","R205_06","R205_07"
  )
) |>
  gt::gt() |>
  gt::tab_header(
    "Item mapping: constructs, source variables and English item descriptions",
    subtitle = paste0("Note: [org] = name of evaluated organisation. ",
                      "Items translated from German; full German wording in research compendium. ",
                      "Reversed items (FC02_10_rev, FC02_12_rev) recoded before analysis.")
  ) |>
  gt::cols_width(Architecture ~ gt::px(120), Construct ~ gt::px(180),
                 Item ~ gt::px(280), `Source variable` ~ gt::px(90)) |>
  gt::tab_style(style=gt::cell_text(weight="bold"),
                locations=gt::cells_column_labels())
```


# Organisations and sampling frame

```{r}
#| label: org-overview
gt::gt(org_synonyme[, c("org_id","org_name")]) |>
  gt::tab_header("Table S1. Austrian NPOs evaluated (n = 26)",
                 subtitle = "Full synonym lists available in R/pipeline/external_Sources.R")
```

```{r}
#| label: source-links
gt::gt(source_links) |>
  gt::tab_header("Table S2. Recruitment channel overview")
```

```{r}
#| label: dataset-registry
#| cache: false
# Table S3: Dataset registry — sample sizes and available outcomes per architecture
purrr::imap_dfr(DATASETS[c("fc","bo","ro","cross")], function(dat, nm) {
  tibble::tibble(
    Dataset      = nm,
    Architecture = c(fc="Faircloth",bo="Boenigk & Becker",
                     ro="Ríos Romero et al.",cross="Cross / Identical-case")[nm],
    Evaluations  = nrow(dat),
    Columns      = ncol(dat),
    `OF02_01 (last donation)`   = sum(!is.na(dat[["OF02_01_num_log"]])),
    `OF02_02 (annual donation)` = sum(!is.na(dat[["OF02_02_num_log"]])),
    `OF_Spender (donor status)` = sum(!is.na(dat[["OF_Spender"]]))
  )
}) |>
  gt::gt() |>
  gt::tab_header(
    "Table S3. Dataset registry — evaluations and outcome availability by architecture",
    subtitle = "Evaluation counts differ because of modular questionnaire routing."
  )
```


# Reliability (omega / CR) and AVE by construct

```{r}
#| label: reliability-ave
#| cache: true
reliability_tbl <- purrr::imap_dfr(cfa_specs, function(s, id) {
  fit <- as_lavaan(fit_cfa(s$syntax, s$data,
                           estimator = "WLSMV", model_id = paste0(id,"_rel")))
  om  <- tryCatch(semTools::compRelSEM(fit, tau.eq = FALSE, return.total = FALSE),
                  error = function(e) tryCatch(semTools::reliability(fit)["omega",],
                                               error = function(e2) NA_real_))
  ave <- tryCatch(semTools::AVE(fit),
                  error = function(e) setNames(rep(NA_real_, length(om)), names(om)))
  tibble::tibble(
    model     = id,
    construct = names(om),
    omega     = round(as.numeric(om), 3),
    AVE       = round(as.numeric(ave[names(om)]), 3),
    AVE_ok    = ifelse(!is.na(AVE), AVE >= .50, NA)
  )
})
save_t(reliability_tbl, "S_reliability_ave")
gt::gt(reliability_tbl) |>
  gt::tab_header("Reliability (omega/CR) and AVE by construct",
                 subtitle = "AVE >= .50 = convergent validity supported")
```


# Sample and non-independence

```{r}
#| label: dataset-sizes
audit <- readr::read_csv(file.path(CSV_DIR, "01_dataset_audit.csv"),
                         show_col_types = FALSE)
gt::gt(audit) |> gt::tab_header("Table S3. Dataset registry audit")
```

```{r}
#| label: icc
#| eval: false
# ICC for the cross-classified structure (respondents × organisations)
if ("REF" %in% names(DATASETS$cross) && "BA03_01" %in% names(DATASETS$cross)) {
  icc_result <- tryCatch(
    icc_crossed(DATASETS$cross, response="OF02_02_num_log",
                group1="REF", group2="BA03_01"),
    error=function(e) { message("ICC error: ", e$message); NULL })
  if (!is.null(icc_result)) {
    message("ICC computed successfully")
    print(icc_result)
  }
} else {
  missing_cols <- setdiff(c("REF","BA03_01"), names(DATASETS$cross))
  message("ICC skipped — missing columns: ", paste(missing_cols, collapse=", "))
  message("Available group columns: ",
          paste(grep("REF|BA03|CASE|ORG", names(DATASETS$cross), 
                     value=TRUE, ignore.case=TRUE), collapse=", "))
}
```

# Discriminant validity (HTMT)

```{r}
#| label: htmt-bo
# Filter to items present in DATASETS$bo (BC03 items may be absent)
bo_items_present <- lapply(construct_items_bo,
  function(its) its[its %in% names(DATASETS$bo)])
bo_items_present <- bo_items_present[sapply(bo_items_present, length) >= 2]
htmt_bo <- htmt_manual(DATASETS$bo, bo_items_present)
save_t(htmt_bo, "S_htmt_boenigk")
gt::gt(htmt_bo) |>
  gt::tab_header("Table S4. Boenigk HTMT (Trust × Commitment)",
                 subtitle = "< .85 acceptable | .85–.90 borderline | > .90 problematic") |>
  gt::fmt_number(columns = c(HTMT, heterotrait_mean, monotrait_1_mean, monotrait_2_mean),
                 decimals = 3)
```

```{r}
#| label: htmt-fc
# Filter to columns present in DATASETS$fc (TOM/SAW may be absent until
# awareness pipeline runs; use available items only)
fc_items_present <- construct_items_fc
fc_items_present <- lapply(fc_items_present,
  function(its) its[its %in% names(DATASETS$fc)])
fc_items_present <- fc_items_present[sapply(fc_items_present, length) >= 2]

htmt_fc <- htmt_manual(DATASETS$fc, fc_items_present)
save_t(htmt_fc, "S_htmt_faircloth")
gt::gt(htmt_fc) |>
  gt::tab_header("Table S5. Faircloth HTMT",
                 subtitle = "Expected borderline: FC_F1 (FC_BR/FC_BD) × FC_F2 (FC_BC/FC_BS)") |>
  gt::fmt_number(columns = c(HTMT, heterotrait_mean, monotrait_1_mean, monotrait_2_mean),
                 decimals = 3)
```

```{r}
#| label: htmt-ro
htmt_ro <- htmt_manual(DATASETS$ro, construct_items_ro)
save_t(htmt_ro, "S_htmt_romero")
gt::gt(htmt_ro) |>
  gt::tab_header("Table S6. Romero HTMT",
                 subtitle = "Expected problematic (> .90): RO_BA–RO_BD, RO_BF–RO_BS, RO_BD–RO_BR") |>
  gt::fmt_number(columns = c(HTMT, heterotrait_mean, monotrait_1_mean, monotrait_2_mean),
                 decimals = 3)
```

```{r}
#| label: htmt-summary
htmt_counts <- dplyr::bind_rows(
  htmt_summary_counts(htmt_bo, "Boenigk & Becker"),
  htmt_summary_counts(htmt_fc, "Faircloth"),
  htmt_summary_counts(htmt_ro, "Romero et al.")
)
save_t(htmt_counts, "S_htmt_summary_counts")
gt::gt(htmt_counts) |> gt::tab_header("Table S7. HTMT interpretation counts by architecture")
```

# Common method variance

```{r}
#| label: cmv-harman
harman_tbl <- dplyr::bind_rows(
  harman_single_factor(
    DATASETS$bo, items = unlist(bo_items_present),
    label = "Boenigk Core Architecture"),
  harman_single_factor(
    DATASETS$fc,
    items = unlist(fc_items_present),
    label = "Faircloth Brand Architecture"),
  harman_single_factor(
    DATASETS$ro, items = unlist(construct_items_ro),
    label = "Romero Complex Architecture")
)
save_t(harman_tbl, "S_cmv_harman")
gt::gt(harman_tbl) |>
  gt::tab_header("Table S8. Harman's single-factor test",
                 subtitle = "Deliberately weak diagnostic; CFA comparison (Table S9) is more informative") |>
  gt::fmt_number(columns = harman_first_var_pct, decimals = 2)
```

```{r}
#| label: cmv-cfa-bo
cmv_bo <- cmv_cfa_comparison(
  trait_model = cfa_bo_original(),
  data        = DATASETS$bo,
  items       = unlist(bo_items_present),
  estimator   = params$ordinal_estimator,
  ordered     = unlist(bo_items_present),
  run_clf     = params$run_clf
)
save_t(cmv_bo, "S_cmv_cfa_boenigk")
gt::gt(cmv_bo) |>
  gt::tab_header("Table S9a. CFA-based CMV comparison — Boenigk",
                 subtitle = "Single-factor CFI expected near .414 vs theoretical .997") |>
  gt::fmt_number(columns = c(chisq, CFI, TLI, RMSEA, SRMR), decimals = 3) |>
  gt::sub_missing(missing_text = "—")
```

```{r}
#| label: cmv-cfa-fc
cmv_fc <- cmv_cfa_comparison(
  trait_model = cfa_fc_higher_order_original(),
  data        = DATASETS$fc,
  items       = unlist(fc_items_present),
  estimator   = params$ordinal_estimator,
  ordered     = unlist(fc_items_present),
  run_clf     = params$run_clf
)
save_t(cmv_fc, "S_cmv_cfa_faircloth")
gt::gt(cmv_fc) |>
  gt::tab_header("Table S9b. CFA-based CMV comparison — Faircloth") |>
  gt::fmt_number(columns = c(chisq, CFI, TLI, RMSEA, SRMR), decimals = 3) |>
  gt::sub_missing(missing_text = "—")
```

```{r}
#| label: cmv-cfa-ro
cmv_ro <- cmv_cfa_comparison(
  trait_model = cfa_ro_original(),
  data        = DATASETS$ro,
  items       = unlist(construct_items_ro),
  estimator   = params$ordinal_estimator,
  ordered     = unlist(construct_items_ro),
  run_clf     = params$run_clf
)
save_t(cmv_ro, "S_cmv_cfa_romero")
gt::gt(cmv_ro) |>
  gt::tab_header("Table S9c. CFA-based CMV comparison — Romero") |>
  gt::fmt_number(columns = c(chisq, CFI, TLI, RMSEA, SRMR), decimals = 3) |>
  gt::sub_missing(missing_text = "—")
```

# Multi-group invariance (donor vs non-donor)

```{r}
#| label: invariance-bo
#| error: true
inv_bo <- tryCatch(invariance_steps(
  model      = cfa_bo_original(),
  data       = DATASETS$bo,
  group      = "OF_Spender",
  estimator  = params$ordinal_estimator,
  ordered    = unlist(bo_items_present)
), error = function(e) { message("invariance-bo failed: ", e$message); NULL })
if (!is.null(inv_bo)) save_t(inv_bo, "S_invariance_boenigk")
gt::gt(inv_bo) |>
  gt::tab_header("Table S10a. Measurement invariance — Boenigk (donor vs non-donor)",
                 subtitle = "Chen (2007): metric/scalar supported if ΔCFI ≥ −.010") |>
  gt::fmt_number(columns = c(CFI, RMSEA, dCFI, dRMSEA), decimals = 3) |>
  gt::sub_missing(missing_text = "—")
```

```{r}
#| label: invariance-fc
#| eval: false
# inv_fc <- invariance_steps(cfa_fc_higher_order_original(), DATASETS$fc,
#                            group="OF_Spender", estimator=params$ordinal_estimator,
#                            ordered=unlist(fc_items_present))
```

```{r}
#| label: invariance-ro
#| eval: false
# inv_ro <- invariance_steps(cfa_ro_original(), DATASETS$ro,
#                            group="OF_Spender", estimator=params$ordinal_estimator,
#                            ordered=unlist(construct_items_ro))
```

> Run this section interactively with the live `validated` object (produced by
> `validate_data()` inside `build_fragebogen()`), or render with
> `rebuild_data: true` so the pipeline runs first.

```{r}
#| label: validation-overview
#| eval: false
# Requires: validated (from build_fragebogen()), config (from settings.R)
source(here::here("R", "pipeline", "settings.R"))
source(here::here("R", "pipeline", "validierung_uebersicht.R"))
# Produces: summary_table (gt) + scorer histogram per questionnaire type
```

```{r}
#| label: validation-summary-table
#| eval: false
# If validated is already in scope:
library(dplyr); library(tibble); library(tidyr)
get_qnr_thresholds <- function(qnr, config) {
  q_cfg <- config$validation$by_qnr[[qnr]]
  list(min_valid_ratio      = q_cfg$min_valid_ratio %||% NA,
       min_duration_q       = q_cfg$min_duration_q  %||% NA,
       max_duration_mult    = config$validation$global$max_duration_multiplier,
       min_score            = config$validation$global$min_score)
}
validated %>%
  group_by(QUESTNNR) %>%
  summarise(n = n(),
            pct_valid        = round(100*mean(is_valid, na.rm=TRUE), 1),
            avg_scorer       = round(mean(scorer,       na.rm=TRUE), 2),
            pct_valid_ratio  = round(100*mean(valid_ratio_score, na.rm=TRUE), 1),
            pct_duration_ok  = round(100*mean(duration_score,    na.rm=TRUE), 1),
            pct_alt_flag     = round(100*mean(alt_score < 0,      na.rm=TRUE), 1),
            .groups = "drop") %>%
  gt::gt() %>%
  gt::tab_header("Table S0. Validation summary by questionnaire type",
                 subtitle = "is_valid threshold: scorer >= 1")
```

# R² difference bootstrap (S20)

```{r}
#| label: bootstrap-read
#| cache: false
#| warning: false
# Read bootstrap results directly — no recomputation needed.
# Tries compendium CSV dir first, then the legacy sem_debug location.
.boot_candidates <- c(
  file.path(CSV_DIR, "supplements", "S20_r2_difference_bootstrap_all_levels.csv"),
  "/home/gerald/10787172/outputs/sem_debug/supplements/S20_r2_difference_bootstrap_all_levels.csv"
)
.boot_csv <- .boot_candidates[file.exists(.boot_candidates)][1]

if (!is.na(.boot_csv) && file.exists(.boot_csv)) {
  boot_tbl <- readr::read_csv(.boot_csv, show_col_types = FALSE)

  boot_tbl |>
    dplyr::select(
      Outcome, Model_A, Model_B,
      R2_A, R2_B, Delta_R2,
      CI_low, CI_high,
      p_value, p_holm,
      B, conv_rate
    ) |>
    dplyr::mutate(
      conv_pct = paste0(round(conv_rate*100,0),"%"),
      dplyr::across(c(R2_A, R2_B, Delta_R2, CI_low, CI_high), ~ round(.x, 3)),
      dplyr::across(c(p_value, p_holm), ~ round(.x, 3))
    ) |>
    gt::gt() |>
    gt::tab_header(
      "Table S11. Bootstrap ΔR² between brand-equity architectures",
      subtitle = paste0(
        "Paired case bootstrap, identical-case sample (n = 266); ",
        "B = 1,000 replicates; MLR+FIML continuous, WLSMV probit binary; ",
        "admissible only (converged, no Heywood); 95% percentile CI; Holm p."
      )
    ) |>
    gt::fmt_number(c(R2_A, R2_B, Delta_R2, CI_low, CI_high), decimals = 3) |>
    gt::fmt_number(c(p_value, p_holm), decimals = 3) |>
    gt::sub_missing(missing_text = "—") |>
    gt::tab_footnote(
      paste0("Romero comparisons: conv_rate 14-18% (137-177 admissible pairs) ",
             "— point estimates and p-values are indicative only."),
      gt::cells_column_labels(conv_pct)
    ) |>
    gt::tab_footnote(
      "Model labels: bo_original = Boenigk & Becker; fc_core_B = Faircloth Core B; ro_original = Ríos Romero et al.",
      gt::cells_column_labels(Model_A)
    )
} else {
  message("Bootstrap CSV not found. Run run_bootstrap.R first.")
  cat("Expected at:
")
  cat(paste(.boot_candidates, collapse = "
"), "
")
}
```

# Faircloth model comparison (AIC/BIC — not a nested chi-square test)

```{r}
#| label: faircloth-nested-correct
#| cache: true
#| error: true
fcA <- as_lavaan(fit_cfa(cfa_specs$fc_higher$syntax, cfa_specs$fc_higher$data,
                         estimator = "WLSMV", model_id = "fc_higher_nested"))
fcB <- as_lavaan(fit_cfa(cfa_specs$fc_coreB$syntax,  cfa_specs$fc_coreB$data,
                         estimator = "WLSMV", model_id = "fc_coreB_nested"))
fmA <- lavaan::fitMeasures(fcA); fmB <- lavaan::fitMeasures(fcB)
nested_tbl <- tibble::tibble(
  model = c("Model A — full attribute set (fc_higher)", "Model B — core, attributes removed (fc_coreB)"),
  CFI   = round(c(dplyr::coalesce(pick(fmA,"cfi.scaled"),pick(fmA,"cfi")),
                  dplyr::coalesce(pick(fmB,"cfi.scaled"),pick(fmB,"cfi"))), 3),
  RMSEA = round(c(dplyr::coalesce(pick(fmA,"rmsea.scaled"),pick(fmA,"rmsea")),
                  dplyr::coalesce(pick(fmB,"rmsea.scaled"),pick(fmB,"rmsea"))), 3),
  SRMR  = round(c(pick(fmA,"srmr"), pick(fmB,"srmr")), 3),
  AIC   = tryCatch(c(AIC(fcA), AIC(fcB)), error = function(e) c(NA_real_, NA_real_)),
  BIC   = tryCatch(c(BIC(fcA), BIC(fcB)), error = function(e) c(NA_real_, NA_real_))
)
save_t(nested_tbl, "S_faircloth_model_comparison")
gt::gt(nested_tbl) |>
  gt::tab_header("Faircloth: descriptive fit comparison",
                 subtitle = "Models A and B differ in indicators -> NOT nested -> no chi-square test permissible")
# Only if truly nested (identical items, B = restriction of A):
# lavaan::lavTestLRT(fcB, fcA, method = "satorra.bentler.2010")
```


# Deviations from the preregistration {#sec-deviations}

**Registered plan:** *Triple Replication Study*, OSF (pre-analysis, post-survey
registration; data collected May–July 2025, registered before analysis;
anonymised view-only link in main text). The registered plan was fixed before
model estimation. The registration governs the *replication* of a single
higher-order path (Brand Equity → Donation Intention); the present manuscript
reuses the same data for a measurement-defensibility comparison and is a
**largely exploratory re-framing** (Bekkers et al., 2025).

| # | Registered plan | As implemented | Type | Rationale |
|---|---|---|---|---|
| 1 | Estimator: MLR primary; WLSMV robustness. | **WLSMV primary** for ordinal measurement models; robust ML for continuous outcomes. | Justified deviation | WLSMV is appropriate for ordinal Likert indicators. |
| 2 | EFA: PAF + varimax. | **Polychoric + OLS** (`psych::fa`); parallel analysis / VSS. | Justified deviation | Correct treatment for ordinal data. |
| 3 | Discriminant validity not specified; comparison via adj. R², ΔCFI/TLI, AIC/BIC. | **HTMT** as primary discriminant criterion. | Exploratory addition | Romero overlap (max HTMT ≈ .96) is therefore exploratory. |
| 4 | Outcome: Brand Equity → Donation Intention (β ≈ .40–.60). | **Realised giving** (most-recent; annual, log) + binary donor status; intention reserved. | Different / expanded | Dashboard question requires behavioural outcomes. |
| 5 | Exclusion: > 60% missing. | **80% / 90% completeness** thresholds. | Justified (stricter) | More conservative analytic sample. |
| 6 | Replication of one higher-order path. | **Architecture-level comparison** → layered dashboard. | Exploratory re-framing | Extends beyond the registered replication. |

**Consistent with the registration:** Austrian online survey, May–July 2025;
>20-organisation, ~2,000-respondent design; constructive-replication logic;
power rationale (Wolf et al., 2013); CFI/TLI/RMSEA/SRMR thresholds;
multi-group reliability/validity across donor/non-donor segments.

```{r}
#| label: robustness-ses
#| eval: false
# SES-adjusted structural models
# Boenigk with SES as covariate on outcomes
tryCatch({
  source(here::here("R", "21_fit_sem.R"))
  ses_bo_raw <- fit_sem(sem_bo_original(), DATASETS$bo,
                    outcome="OF02_02_num_log", ses_mode="outcome")
  ses_bo <- tryCatch(as_lavaan(ses_bo_raw), error=function(e) NULL)
  if (!is.null(ses_bo) && !inherits(ses_bo, "error") &&
      lavaan::lavInspect(ses_bo,"converged")) {
    fm <- lavaan::fitMeasures(ses_bo, c("cfi","rmsea","srmr"))
    r2  <- lavaan::lavInspect(ses_bo,"r2")[["OF02_02_num_log"]]
    message(sprintf("Boenigk SES-adjusted: CFI=%.3f RMSEA=%.3f R²=%.3f",
                    fm["cfi"], fm["rmsea"], r2))
    std <- lavaan::standardizedSolution(ses_bo)
    std[std$op=="~", c("lhs","rhs","est.std","pvalue")] |>
      gt::gt() |>
      gt::tab_header("SES-adjusted Boenigk model — structural paths",
                     subtitle="Annual donation, MLR, SES as outcome covariate")
  } else {
    message("Boenigk SES model: not converged or error — skipping display")
  }
}, error=function(e) message("SES model error: ", e$message))
```

```{r}
#| label: robustness-alt-structures
#| eval: false
# Alternative Faircloth structures: Core B and Purified A
tryCatch({
  for (spec in list(
    list(fn=cfa_fc_core_B,     id="fc_coreB",  label="Faircloth Core B"),
    list(fn=cfa_fc_purified_A, id="fc_purA",   label="Faircloth Purified A")
  )) {
    fit_alt <- fit_cfa(spec$fn(), DATASETS$fc,
                       estimator=params$ordinal_estimator, model_id=spec$id)
    fit_lav <- tryCatch(as_lavaan(fit_alt), error=function(e) NULL)
    if (!is.null(fit_lav) && lavaan::lavInspect(fit_lav,"converged")) {
      fm <- lavaan::fitMeasures(fit_lav, c("cfi","tli","rmsea","srmr","aic"))
      message(sprintf("%s: CFI=%.3f TLI=%.3f RMSEA=%.3f SRMR=%.3f AIC=%.0f",
                      spec$label, fm["cfi"],fm["tli"],fm["rmsea"],fm["srmr"],fm["aic"]))
    }
  }
}, error=function(e) message("Alternative Faircloth error: ", e$message))
```

# Exploratory Integration: BBB / BUB / BRB (Chatzi framework)

> This section is exploratory and confined to the Faircloth + Boenigk
> architectures (shared qnr1 sample, n = 2,038). Full analysis in
> `analysis/06_exploratory_fc_bo_model.qmd`.

```{r}
#| label: chatzi-summary
#| cache: false
#| eval: true
# Read Stage 3b comparison from CSV if available, else show static table
chatzi_csv <- file.path(CSV_DIR, "S_chatzi_block_comparison.csv")
if (file.exists(chatzi_csv)) {
  readr::read_csv(chatzi_csv, show_col_types=FALSE) |>
    gt::gt() |>
    gt::tab_header("BBB/BUB/BRB block assignment comparison (AIC-based)",
                   subtitle="Best: Version B — AW in BBB (ΔAIC=4 vs AW in BUB)")
} else {
  # Static summary from rendered 06 output
  tibble::tibble(
    Version = c("A: AW in BUB (Chatzi original)",
                "B: AW in BBB (empirically preferred)",
                "2-block (BBB+BRB, no BUB)"),
    BUB = c("FC_BF + AW + FC_BR", "FC_BF + FC_BR", "absorbed into BBB"),
    BBB = c("FC_BD + FC_BC", "FC_BD + FC_BC + AW", "FC_BD + FC_BC + AW + FC_BR + FC_BF"),
    CFI   = c(.917, .917, .916),
    RMSEA = c(.075, .075, .075),
    AIC   = c(227493L, 227489L, 227555L)
  ) |>
    gt::gt() |>
    gt::tab_header(
      "BBB/BUB/BRB block assignment: fit comparison (FC + BO, n = 2,038)",
      subtitle = paste0(
        "Optimal: AW (TOM+SAW) in Brand Building Block — ΔAIC = 4 vs BUB. ",
        "3-block outperforms 2-block by ΔAIC = 62."
      )
    ) |>
    gt::fmt_number(c(CFI, RMSEA), decimals=3) |>
    gt::fmt_integer(AIC)
}
```

**Interpretation.** Brand awareness (TOM+SAW) is empirically better assigned to
the Brand Building Block (BBB) than to Brand Understanding (BUB), consistent
with the view that awareness is an *output* of brand-building activities rather
than a passive perceptual input. The three-block structure (BBB→BUB→BRB) is
well-supported over a two-block collapse (ΔAIC = 62), suggesting empirically
separable brand-equity strata. The second-order loadings are:

| Block | Indicator | λ | p |
|---|---|---|---|
| **BUB** (Understanding) | FC_BF (Familiarity) | .47 | <.001 |
| **BUB** | AW→**BBB** in opt. | .37→loaded on BBB | — |
| **BUB** | FC_BR (Recall) | .95 | <.001 |
| **BBB** (Building) | FC_BD (Differentiation) | .78 | <.001 |
| **BBB** | FC_BC (Commitment) | .74 | <.001 |
| **BRB** (Relationship) | BO_TR (Trust) | .85 | <.001 |
| **BRB** | BO_CO (Commitment) | .71 | <.001 |

Classical SEM with all three blocks as parallel predictors of annual donation
(CFI=.916, RMSEA=.073, R²=.137): BBB→Donation β=+.920 (p<.001), BUB→Donation
β=−.077 (ns), BRB→Donation β=−.370 (p=.021, suppressor when BBB present).


# Session info {.unnumbered}

```{r}
#| label: sessioninfo
#| eval: !expr knitr::is_latex_output() == FALSE
#| include: !expr knitr::is_latex_output() == FALSE
sessionInfo()
```

# References {.unnumbered}

Bekkers, R., Chapman, C. M., Prosser, A. M. B., Wiepking, P., & Meyer, M.
(2025). Let us be clear: Why and how to demonstrate data and methods
transparency in nonprofit research. *VOLUNTAS, 36*(4), 473–482.
https://doi.org/10.1007/s11266-025-00736-0
